\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{booktabs}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}

\lstdefinestyle{bash}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  frame=single,
  backgroundcolor=\color{gray!5}
}
\lstdefinestyle{json}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  frame=single,
  backgroundcolor=\color{gray!5}
}
\lstdefinestyle{sql}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  frame=single,
  backgroundcolor=\color{gray!5}
}

\title{\textbf{ByteVault Project Documentation}}
\author{ByteVault Team}
\date{\today}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{Overview}
ByteVault is a banking management application with:
\begin{itemize}[nosep]
  \item A \textbf{Next.js} client (frontend).
  \item A \textbf{Bun + Express} API server (backend).
  \item \textbf{Two PostgreSQL 16} databases (Main branch and Sub branch) running in Docker.
  \item Cross-database integration using \textbf{Foreign Data Wrapper (FDW)} and cross-branch settlement correctness using \textbf{Two-Phase Commit (2PC)}.
\end{itemize}

\section{Goals and Constraints}
\subsection{Banking correctness goals}
\begin{itemize}[nosep]
  \item \textbf{ACID}: transactional correctness for all money movements.
  \item \textbf{Idempotency}: all payment/transfer routes accept idempotency keys to prevent duplicate execution.
  \item \textbf{Auditability}: sensitive operations are written to an audit log.
  \item \textbf{Maker/Checker}: transfer requests are created by Maker and executed only after Checker approval.
\end{itemize}

\subsection{Architecture constraints}
\begin{itemize}[nosep]
  \item Main branch DB is \textbf{local} and imports Sub branch tables via FDW (\texttt{fdw\_sub.*}).
  \item Schemas are mirrored between Main and Sub.
  \item Backend communicates to each DB using separate connection strings.
\end{itemize}

\section{Repository Layout}
\begin{longtable}{@{}ll@{}}
\toprule
Path & Purpose \\
\midrule
\texttt{docker-compose.yml} & Starts Main and Sub Postgres containers \\
\texttt{docker/init.sql} & Schema bootstrap (mirrored tables + FDW setup on Main) \\
\texttt{docker/custom.conf} & Postgres runtime config (timeouts, listen\_addresses, 2PC) \\
\texttt{docker/apply-*.sql} & Apply migrations to existing DB volumes \\
\texttt{backend/} & Bun + Express API server \\
\texttt{client/} & Next.js frontend \\
\bottomrule
\end{longtable}

\section{Databases}
\subsection{Containers}
Two Postgres containers are used:
\begin{itemize}[nosep]
  \item \textbf{Main DB}: \texttt{branch\_a\_db} (container \texttt{bytevault\_branch\_a})
  \item \textbf{Sub DB}: \texttt{branch\_b\_db} (container \texttt{bytevault\_branch\_b})
\end{itemize}

\subsection{FDW}
Main imports a subset of Sub tables into schema \texttt{fdw\_sub}:
\begin{itemize}[nosep]
  \item \texttt{branches}, \texttt{users}, \texttt{employees}, \texttt{accounts}, \texttt{transactions}, \texttt{external\_transfers}
\end{itemize}

This enables Main to resolve Sub entities without direct Sub DB access from the client.

\subsection{2PC}
Cross-branch settlement uses Postgres prepared transactions:
\begin{itemize}[nosep]
  \item \texttt{PREPARE TRANSACTION}
  \item \texttt{COMMIT PREPARED} / \texttt{ROLLBACK PREPARED}
\end{itemize}

\textbf{Important:} Postgres must have \texttt{max\_prepared\_transactions > 0}. This is configured in \texttt{docker/custom.conf}.

\subsection{Core schema (high-level)}
The schema includes:
\begin{itemize}[nosep]
  \item Operational tables: \texttt{branches}, \texttt{users}, \texttt{employees}, \texttt{accounts}
  \item Transfer workflow: \texttt{transfer\_requests} (maker/checker)
  \item Idempotency: \texttt{idempotency\_keys}
  \item Auditing: \texttt{audit\_logs}
  \item Ledger (double-entry): \texttt{ledger\_accounts}, \texttt{journal\_entries}, \texttt{journal\_lines}
\end{itemize}

\section{Backend (Bun + Express)}
\subsection{Runtime configuration}
Backend reads environment variables from \texttt{backend/.env}. Example:
\begin{lstlisting}[style=bash]
PORT=4000
BRANCH_A_DB_URL=postgresql://admin_a:secure_password_a@localhost:55432/branch_a_db
BRANCH_B_DB_URL=postgresql://admin_b:secure_password_b@localhost:55433/branch_b_db
JWT_SECRET=change_me_to_a_long_random_string
JWT_ISSUER=bytevault
JWT_AUDIENCE=bytevault-client
\end{lstlisting}

\subsection{Logging and debugging}
Every request logs:
\begin{itemize}[nosep]
  \item request start/end
  \item correlation id \texttt{x-request-id}
  \item method, path, status, latency (ms)
  \item employee id/role (when authenticated)
\end{itemize}

\subsection{Health endpoints}
\begin{itemize}[nosep]
  \item \texttt{GET /health}: basic liveness
  \item \texttt{GET /health/deep}: DB A, DB B, FDW presence, 2PC readiness
\end{itemize}

\subsection{Authentication and RBAC}
\begin{itemize}[nosep]
  \item Employee login issues JWT access tokens.
  \item RBAC roles: \texttt{MAKER}, \texttt{CHECKER}, \texttt{MANAGER}, \texttt{ADMIN}
  \item Authorization is enforced server-side using middleware.
\end{itemize}

\subsection{Idempotency}
Payment/transfer routes require an \texttt{Idempotency-Key} header. The backend:
\begin{itemize}[nosep]
  \item stores request hash and response snapshot
  \item returns prior response on repeated requests (same key, same body)
  \item marks failures as \texttt{FAILED} to avoid stuck \texttt{IN\_PROGRESS}
\end{itemize}

\subsection{Current API surface (summary)}
\paragraph{Auth}
\begin{itemize}[nosep]
  \item \texttt{POST /api/auth/employee/login}
  \item \texttt{GET /api/auth/me}
\end{itemize}

\paragraph{Users}
\begin{itemize}[nosep]
  \item \texttt{POST /api/users}
  \item \texttt{GET /api/users?limit=\dots\&offset=\dots}
  \item \texttt{GET /api/users/:id}
\end{itemize}

\paragraph{Accounts}
\begin{itemize}[nosep]
  \item \texttt{POST /api/accounts}
  \item \texttt{GET /api/accounts?limit=\dots\&offset=\dots}
  \item \texttt{GET /api/accounts/:id}
  \item \texttt{GET /api/accounts/by-number/:accountNumber}
\end{itemize}

\paragraph{Transfers (Maker/Checker)}
\begin{itemize}[nosep]
  \item \texttt{POST /api/transfers/requests} (Maker)
  \item \texttt{POST /api/transfers/requests/:id/approve} (Checker; executes 2PC)
  \item \texttt{POST /api/transfers/requests/:id/reject} (Checker)
  \item \texttt{GET /api/transfers/requests}
\end{itemize}

\paragraph{Ledger (Admin only for now)}
\begin{itemize}[nosep]
  \item \texttt{POST /api/ledger/entries}
  \item \texttt{GET /api/ledger/entries/:id}
  \item \texttt{GET /api/ledger/customer-accounts/:bankAccountId/balance}
  \item \texttt{POST /api/ledger/customer-accounts/:bankAccountId/sync-to-cached} (Admin)
\end{itemize}

\section{Ledger (Double-Entry Accounting)}
\subsection{Concept}
Money movement is represented as a \textbf{journal entry} with multiple \textbf{journal lines}:
\[
\sum_{i=1}^{n} \text{amount\_cents}_i = 0
\]

Lines are signed integers in cents:
\begin{itemize}[nosep]
  \item Positive = credit
  \item Negative = debit
\end{itemize}

\subsection{Ledger accounts}
\begin{itemize}[nosep]
  \item \texttt{CUSTOMER}: one ledger account per customer bank account (\texttt{ref\_account\_id})
  \item \texttt{INTERNAL}: internal buckets (fees, suspense, clearing)
\end{itemize}

\subsection{Posting}
Posting is performed in a SQL transaction:
\begin{itemize}[nosep]
  \item validate balanced lines
  \item insert \texttt{journal\_entries}
  \item insert \texttt{journal\_lines}
\end{itemize}

\subsection{Cached balance compatibility}
During the transition to a ledger-first system, \texttt{accounts.balance} is treated as a \textbf{cached} value for compatibility. The system supports:
\begin{itemize}[nosep]
  \item Auto-creation of an \texttt{OPENING\_BALANCE} entry (idempotent, per account) so ledger and cache start aligned.
  \item A privileged sync endpoint (\texttt{sync-to-cached}) which posts a balanced adjustment entry if drift is detected.
\end{itemize}

\subsection{Inter-branch transfer template (Phase 1)}
For inter-branch settlement with 2PC, transfers currently post balanced entries in both DBs using an internal clearing account:
\begin{itemize}[nosep]
  \item \textbf{Main DB} (\texttt{TRANSFER\_OUT}): debit customer / credit clearing
  \item \textbf{Sub DB} (\texttt{TRANSFER\_IN}): debit clearing / credit customer
\end{itemize}
This keeps each database internally consistent while 2PC ensures both sides commit together.

\section{How to Run (Development)}
\subsection{Databases}
From repo root:
\begin{lstlisting}[style=bash]
docker compose up -d
docker compose ps
\end{lstlisting}

\subsection{Backend}
\begin{lstlisting}[style=bash]
cd backend
bun install
cp .env.example .env
bun run dev
\end{lstlisting}

\subsection{Client}
\begin{lstlisting}[style=bash]
cd client
npm install
cp .env.example .env.local
npm run dev
\end{lstlisting}

\section{Operational Notes}
\subsection{Applying migrations to existing volumes}
If DB volumes already exist, apply incremental scripts:
\begin{lstlisting}[style=bash]
docker compose exec -T branch_a_db psql -U admin_a -d branch_a_db < docker/apply-security.sql
docker compose exec -T branch_b_db psql -U admin_b -d branch_b_db < docker/apply-security.sql

docker compose exec -T branch_a_db psql -U admin_a -d branch_a_db < docker/apply-ledger.sql
docker compose exec -T branch_b_db psql -U admin_b -d branch_b_db < docker/apply-ledger.sql
\end{lstlisting}

\subsection{Deep health check}
\begin{lstlisting}[style=bash]
curl http://localhost:4000/health/deep
\end{lstlisting}

\section{Next Implementation Milestones}
\begin{enumerate}[nosep]
  \item Phase 1: Post ledger entries for transfers under 2PC (keep cached balance for compatibility). \textbf{Done}.
  \item Phase 1: Add ledger-derived balance endpoints and drift detection/sync. \textbf{Done}.
  \item Phase 1: Move insufficient-funds checks to ledger-derived available balance (introduce holds/authorizations).
  \item Add internal ledger accounts (clearing/suspense/fees) and formalize transfer entry templates.
  \item Add reversals (immutable corrections) and reconciliation tooling.
  \item Add integration tests for ledger invariants, idempotency, and 2PC failure modes.
\end{enumerate}

\end{document}

