\section{Overview}
ByteVault is a mission-critical core banking system designed for high reliability and transactional integrity across distributed branches. It serves as a unified platform for managing user accounts, ledger operations, and cross-branch fund transfers.

\subsection{Key Components}
\begin{itemize}
  \item \textbf{Frontend (Client)}: A modern, responsive \textbf{Next.js} dashboard for employees and administrators, featuring real-time data visualization and secure workflow management.
  \item \textbf{Backend (Server)}: A high-performance \textbf{Bun + Express} API server that handles business logic, authentication, and database orchestration.
  \item \textbf{Distributed Databases}: Two \textbf{PostgreSQL 16} instances representing geographically distinct branches (Main and Sub), containerized for consistent deployment via Docker.
\end{itemize}

\subsection{Technology Justification: Why Next.js?}
The frontend architecture utilizes \textbf{Next.js} over standard Single Page Application (SPA) libraries like basic React or Vue. This decision was driven by the need for:
\begin{itemize}
    \item \textbf{Server-Side Rendering (SSR)}: Financial dashboards require rapid First Contentful Paint (FCP) and secure, server-side data fetching to prevent sensitive API endpoints from being exposed in client-side bundles.
    \item \textbf{Middleware and Proxies}: Next.js provides robust Edge Middleware capabilities, allowing the application to intercept, validate, and proxy requests to the Bun backend securely without CORS complexities.
    \item \textbf{App Router Architecture}: The nested routing system cleanly separates employee workflows (e.g., Maker vs. Checker vs. Admin) into distinct, easily auditable layout boundaries.
\end{itemize}

\subsection{Differentiating Technologies}
The system employs advanced database patterns to solve common distributed banking problems:
\begin{itemize}
  \item \textbf{Foreign Data Wrapper (FDW)}: Enables the Main branch to query Sub branch data natively, allowing for unified reporting and simplified cross-branch lookups.
  \item \textbf{Two-Phase Commit (2PC)}: Guarantees atomicity for cross-branch transfers. Money is never "lost" between databases; either both branches commit the transaction or both roll back, even in the event of a partial system failure.
  \item \textbf{Double-Entry Ledger}: All financial operations are backed by a robust ledger system (Journal Entries and Lines), ensuring that the total balance across all accounts is always zero-sum and auditable.
\end{itemize}
