\section{Ledger (Double-Entry Accounting)}
\subsection{Concept}
Money movement is represented as a \textbf{journal entry} with multiple \textbf{journal lines}:
\[
\sum_{i=1}^{n} \text{amount\_cents}_i = 0
\]

Lines are signed integers in cents:
\begin{itemize}[nosep]
  \item Positive = credit
  \item Negative = debit
\end{itemize}

\subsection{Ledger accounts}
\begin{itemize}[nosep]
  \item \texttt{CUSTOMER}: one ledger account per customer bank account (\texttt{ref\_account\_id})
  \item \texttt{INTERNAL}: internal buckets structured to balance organizational assets. The standardized \texttt{INTERNAL\_ACCOUNTS} registry currently includes:
  \begin{itemize}[nosep]
    \item \texttt{CLEARING\_INTERBRANCH}: Used to settle balances momentarily between the Main and Sub branches during 2PC execution.
    \item \texttt{SUSPENSE\_GENERAL}: General suspense account for holding funds pending manual reconciliation.
    \item \texttt{FEE\_REVENUE}: Tracks platform fee revenue from charged services.
  \end{itemize}
\end{itemize}

\subsection{Posting}
Posting is performed in a SQL transaction:
\begin{itemize}[nosep]
  \item validate balanced lines
  \item insert \texttt{journal\_entries}
  \item insert \texttt{journal\_lines}
\end{itemize}

\subsection{Cached balance compatibility}
During the transition to a ledger-first system, \texttt{accounts.balance} is treated as a \textbf{cached} value for compatibility. The system supports:
\begin{itemize}[nosep]
  \item Auto-creation of an \texttt{OPENING\_BALANCE} entry (idempotent, per account) so ledger and cache start aligned.
  \item A privileged sync endpoint (\texttt{sync-to-cached}) which posts a balanced adjustment entry if drift is detected.
\end{itemize}

\subsection{Insufficient-Funds Checks (Holds)}
When a transfer request is created by a Maker, the backend checks the ledger's accumulated journal lines minus any active \textbf{holds/authorizations}. If funds are sufficient, an \texttt{account\_holds} record with \texttt{status='ACTIVE'} is created and linked to the pending \texttt{transfer\_request}. During execution (Checker approval), the hold is transitioned to \texttt{CAPTURED}. On rejection, the hold is \texttt{RELEASED}.

\subsection{Formalized Transfer Templates}
To reduce error and guarantee balanced postings across diverse financial events, journal entry creation is strictly funneled through standardized templates within \texttt{backend/src/ledger/templates.ts}.

For inter-branch settlement under 2PC, transfers utilize two synchronized templates representing the distributed clearing pipeline:
\begin{itemize}[nosep]
  \item \textbf{Main DB} (\texttt{postInterBranchTransferOutTemplate}): Debits CUSTOMER, credits \texttt{CLEARING\_INTERBRANCH}.
  \item \textbf{Sub DB} (\texttt{postInterBranchTransferInTemplate}): Debits \texttt{CLEARING\_INTERBRANCH}, credits CUSTOMER.
\end{itemize}

Additional templates are also formalized for automated actions, including \texttt{postFeeTemplate} and \texttt{postSuspenseTemplate}, keeping the transaction controllers oblivious to manual accounting parameters and ensuring mathematical soundness at scale.

\subsection{Reversals (Immutable Corrections)}
An entry is never deleted. Corrections are applied by posting a \textbf{reversal entry} that mirrors the original lines with inverted amounts.

Schema support:
\begin{itemize}[nosep]
  \item \texttt{journal\_entries.reversal\_of\_entry\_id} --- nullable FK back to the original entry.
  \item \texttt{UNIQUE(reversal\_of\_entry\_id)} --- prevents double-reversal of the same entry.
\end{itemize}

Endpoint: \texttt{POST /api/ledger/entries/:id/reverse}
\begin{itemize}[nosep]
  \item Requires \texttt{ADMIN} role, idempotency key, and a mandatory \texttt{reason} string.
  \item Rejects attempts to reverse a \texttt{REVERSAL} entry (400).
  \item Returns \texttt{409 Conflict} if the entry has already been reversed (unique constraint catch).
\end{itemize}

\subsection{Reconciliation Tooling}
A materialized view \texttt{ledger\_daily\_balances} pre-aggregates journal lines by ledger account and date to avoid full-table scans during reporting.

Endpoint: \texttt{GET /api/ledger/reconciliation/report?start\_date=\dots\&end\_date=\dots}
\begin{itemize}[nosep]
  \item Requires \texttt{ADMIN} role.
  \item Returns net balance in cents for each \texttt{INTERNAL} ledger account within the date range.
  \item Clearing accounts should net to zero; non-zero values indicate unsettled discrepancies.
\end{itemize}

\subsection{Transaction Hardening}
Several critical safety measures are enforced in the 2PC execution path:
\begin{itemize}[nosep]
  \item \textbf{Row-count validation}: Cached balance updates (\texttt{UPDATE accounts}) are verified via \texttt{rowCount}. A zero-row update on either branch throws immediately, preventing silent fund loss.
  \item \textbf{2PC phase separation}: A \texttt{phase2} flag tracks whether \texttt{COMMIT PREPARED} has begun. After entering phase 2, the catch block never issues \texttt{ROLLBACK PREPARED}, preventing partial-commit / partial-rollback split-brain states.
  \item \textbf{Crash-safe approval}: The \texttt{APPROVED} status is committed atomically before releasing the row lock and before invoking \texttt{execute2pcTransfer}. If the process crashes mid-2PC, the request is already \texttt{APPROVED}, preventing re-approval and double-spend.
  \item \textbf{Hold release on failure}: If the 2PC execution fails, the catch block releases the associated \texttt{account\_holds} record to prevent permanent fund locking.
  \item \textbf{Connection pool limits}: Both pools enforce \texttt{max: 20}, \texttt{idleTimeoutMillis: 30000}, and \texttt{connectionTimeoutMillis: 2000}.
  \item \textbf{Currency as string}: The Maker route accepts \texttt{amount} as a string, validated via regex (\texttt{/\^{}\textbackslash d+(\textbackslash.\textbackslash d\{1,2\})?\$/}), eliminating IEEE 754 floating-point precision loss.
\end{itemize}
