\section{Operational Notes}
\subsection{Applying migrations to existing volumes}
If DB volumes already exist, apply incremental scripts:
\begin{lstlisting}[style=bash]
docker compose exec -T branch_a_db psql -U admin_a -d branch_a_db < docker/apply-security.sql
docker compose exec -T branch_b_db psql -U admin_b -d branch_b_db < docker/apply-security.sql

docker compose exec -T branch_a_db psql -U admin_a -d branch_a_db < docker/apply-ledger.sql
docker compose exec -T branch_b_db psql -U admin_b -d branch_b_db < docker/apply-ledger.sql

docker compose exec -T branch_a_db psql -U admin_a -d branch_a_db < docker/apply-holds.sql
docker compose exec -T branch_b_db psql -U admin_b -d branch_b_db < docker/apply-holds.sql

cat docker/apply-transfer-holds.sql | docker compose exec -T branch_a_db psql -U admin_a -d branch_a_db
cat docker/apply-transfer-holds.sql | docker compose exec -T branch_b_db psql -U admin_b -d branch_b_db

cat docker/apply-reversals.sql | docker compose exec -T branch_a_db psql -U admin_a -d branch_a_db
cat docker/apply-reversals.sql | docker compose exec -T branch_b_db psql -U admin_b -d branch_b_db
\end{lstlisting}

\subsection{Deep health check}
\begin{lstlisting}[style=bash]
curl http://localhost:4000/health/deep
\end{lstlisting}
\subsection{Compliance (KYC) Dashboard}
The system tracks the Know Your Customer (KYC) status for all users. Statuses include:
\begin{itemize}
    \item \textbf{PENDING}: Initial state for new users.
    \item \textbf{VERIFIED}: User is cleared for full banking operations.
    \item \textbf{REJECTED}: User is blocked from opening new accounts or transacting.
\end{itemize}
These statuses are displayed as visual badges in the \texttt{AccountsTable} on the employee dashboard.

\subsection{Operational Audit Trail}
Every sensitive action in ByteVault is captured in the \texttt{audit\_logs} table. This includes:
\begin{itemize}
    \item Account creations and status changes.
    \item Transfer requests and approvals.
    \item Manual ledger adjustments.
\end{itemize}
Admin users can view the full history at \texttt{/admin/audit}, which displays the actor UUID, action type, entity involved, and associated metadata.

\subsubsection{Technical Implementation Details}
The recent compliance update introduced several system-wide enhancements to support these operational views:
\begin{itemize}
    \item \textbf{TypeScript Definitions}: The \texttt{AccountRow} interface in the Next.js client was updated to accept flexible string typings (\texttt{kyc\_status?: string;}) to ensure forward compatibility with new compliance statuses.
    \item \textbf{SQL Optimization}: The backend endpoint for single-account queries (\texttt{GET /api/accounts/by-number/:accountNumber}) was optimized to perform a \texttt{JOIN} with the \texttt{users} table. This guarantees that \texttt{kyc\_status} is efficiently returned alongside account details without N+1 query problems.
    \item \textbf{Route Mounting}: A dedicated \texttt{auditRouter} is now mounted at \texttt{/api/audit} to stream the \texttt{audit\_logs} table directly to the frontend.
    \item \textbf{Navigation Injection}: The employee dashboard navigation bar (\texttt{navbar.tsx}) dynamically injects a \texttt{<LayoutDashboard />} icon linking to the Audit Trail strictly for users authenticated with the \texttt{ADMIN} role.
    \item \textbf{Seeding Infrastructure}: The development environment features an updated \texttt{seed-demo.ts} script that rapidly provisions verified/rejected users and floods the audit table with diverse events (e.g., \texttt{TRANSFER\_APPROVED}, \texttt{KYC\_REVIEWED}) to properly simulate production volume.
\end{itemize}
